Phenotypic evolution is more constrained in simpler food webs

### 2019-01-11 manuscript.Rmd
adjust affiliation order and manuscript elements.

---
title: Phenotypic evolution is more constrained in simpler food webs
author: 
- Matthew A. Barbour$^{1,2,\ast}$
- Christopher J. Greyson-Gaito$^{1,3}$ 
- Arezoo Sootodeh$^{3}$ 
- Brendan Locke$^{4}$ 
- Jordi Bascompte$^{2}$
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

\noindent 1. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada; <!-- consider removing -->

\noindent 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;

@@

*Manuscript elements*: Figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.

>>>>

---
title: Phenotypic evolution is more constrained in simpler food webs
author: 
- Matthew A. Barbour$^{1,2,\ast}$
- Christopher J. Greyson-Gaito$^{1,3}$ 
- Arezoo Sootodeh$^{2}$ 
- Brendan Locke$^{4}$ 
- Jordi Bascompte$^{1}$
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

@@

\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;

\noindent 2. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada;

@@

*Manuscript elements*: Table 1, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
